MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-06-06 MAESTROeX_I/results.tex
fixed typo

We continue to use the full-star white dwarf problem described in Section \ref{sec:whitedwarf} to test adaptive simulations on spherical geometry. The adaptive grid is refined twice by tagging the density at $\rho < 5\times 10^7$ g cm$^{-3}$ on the first level and $\rho < 10^8$ g cm$^{-3}$ on the second level. The simulation on a single-level grid of $512^3$ resolution took 26.01 s per time step (again averaged over 10 time steps).  The adaptive grid has a resolution of $128^3$ at the coarsest level and an effective resolution of $512^3$ at the finest level. On this grid, 8.9\% of the cells (1,493,504 out of $256^3$ cells) are refined at the first level and 5.3\% (7,176,192 out of $512^3$ cells) at the second. The adaptive simulation took 11.55 s, resulting in more than a factor of 2 in speedup. Both simulations are computed to $t=400$ s and we choose to use the peak temperature as the diagnostics to compare the results. Figure \ref{fig:wdconvect_amr_Tmax} shows the evolution of the peak temperature for all three runs and shows that the adaptive simulation gives the same qualitative result as the single-level simulation. We do not expect the curves to match up exactly because the governing equations are highly nonlinear, and slight differences in the solution caused by solver tolerance and discretization error can change the details of the results. Each simulation was run on Cori KNL with 512 processors and 16 threads per core.

>>>>

We continue to use the full-star white dwarf problem described in Section \ref{sec:whitedwarf} to test adaptive simulations on spherical geometry. The adaptive grid is refined twice by tagging the density at $\rho > 5\times 10^7$ g cm$^{-3}$ on the first level and $\rho > 10^8$ g cm$^{-3}$ on the second level. The simulation on a single-level grid of $512^3$ resolution took 26.01 s per time step (again averaged over 10 time steps).  The adaptive grid has a resolution of $128^3$ at the coarsest level and an effective resolution of $512^3$ at the finest level. On this grid, 8.9\% of the cells (1,493,504 out of $256^3$ cells) are refined at the first level and 5.3\% (7,176,192 out of $512^3$ cells) at the second. The adaptive simulation took 11.55 s, resulting in more than a factor of 2 in speedup. Both simulations are computed to $t=400$ s and we choose to use the peak temperature as the diagnostics to compare the results. Figure \ref{fig:wdconvect_amr_Tmax} shows the evolution of the peak temperature for all three runs and shows that the adaptive simulation gives the same qualitative result as the single-level simulation. We do not expect the curves to match up exactly because the governing equations are highly nonlinear, and slight differences in the solution caused by solver tolerance and discretization error can change the details of the results. Each simulation was run on Cori KNL with 512 processors and 16 threads per core.
